The \dealii Library, Version 9.7

### 2025-07-29 9.7/paper.tex
Add a todo
Update Kokkos

@@

\subsubsection{Kokkos, a performance portability library}
\label{subsec:external-kokkos}

Kokkos is a C++ library that makes it easy to write codes that can
portably run on CPUs and GPUs of different vendors, using their
respective underlying programming models.
The \dealii{} 9.5 release~\cite{dealII95} made \kokkos~\cite{trott2022} a required
dependency. The current release removes the deprecated \texttt{CUDAWrappers} namespace as well
as all \texttt{CUDA}-related macros in favor of Kokkos
equivalents.

\todo[inline]{Now
  bundling Kokkos 4.5.1; are we using something new from Kokkos?}

@@

  \item As already mentioned in
    Section~\ref{subsec:external-kokkos}, the current release
    removes the deprecated \texttt{CUDAWrappers} namespace as well 
    as all \texttt{CUDA}-related macros in favor of Kokkos
    equivalents.

>>>>

\todo[inline]{There were several changes in Portable::MatrixFree: support for
multiple components, generalization to fe degree less than n q points 1d,
support for DeviceVector and BlockVector}

@@

\subsubsection{\kokkos, a performance portability library}
\label{subsec:external-kokkos}

\kokkos is a C++ library that makes it easy to write codes that can
portably run on CPUs and GPUs of different vendors, using their
respective underlying programming models.
The \dealii{} 9.5 release~\cite{dealII95} made \kokkos~\cite{trott2022} a required
dependency. The current release removes the deprecated \texttt{CUDAWrappers} namespace as well
as all \texttt{CUDA}-related macros in favor of \kokkos
equivalents. The 9.7 release now bundles \kokkos 4.5.1 but the minimum version required is still 3.4.

@@

  \item As already mentioned in
    Section~\ref{subsec:external-kokkos}, the current release
    removes the deprecated \texttt{CUDAWrappers} namespace as well 
    as all \texttt{CUDA}-related macros in favor of \kokkos
    equivalents.
